Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-04-16 paper/main.tex
add bits
paper
update

\author{Manuel López-Ibáñez}
\orcid{0000-0001-9974-1295}
\affiliation{
  \institution{University of Málaga}
  \city{Málaga}
  \country{Spain}
}
\additionalaffiliation{University of Manchester, UK}
\email{manuel.lopez-ibanez@uma.es}

@@

\begin{figure}[!tb]
  \centering%
  \smaller
\begin{minipage}{0.49\linewidth}
  \centering
    \texttt{N-t59d11xx} (LOP)\\[-0.2ex]
    \includegraphics[width=\textwidth]{../img/heatmap_lop_IO_N-t59d11xx}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}
    \centering
    \texttt{N-sgb75.02} (LOP)\\[-0.2ex]
 \includegraphics[width=\textwidth]{../img/heatmap_lop_SGB_N-sgb75_02}
\end{minipage}\\\vskip 1em
\begin{minipage}{0.49\linewidth}
  \centering
  \texttt{reC13} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/heatmap_pfsp_rec13_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \centering
  \texttt{reC19} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/heatmap_pfsp_rec19_txt}
\end{minipage}
% \begin{minipage}{0.49\linewidth}
%   \centering
%   \texttt{kra32} (QAP)\\[-0.5ex]
% \includegraphics[width=\textwidth]{../img/heatmap_kra32_dat}
% \end{minipage}
\caption{Mean fitness (over 10 runs) of different configurations of $r_1$ and $r_2$ (darker is better).\label{fig:heatmaps}}
\end{figure}

@@

%  \includegraphics[width=\textwidth]{../img/synthetic_LOP_combined}

@@

%  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandB_N-p50-01}\\
%  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d100_01}\\
%  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d150_01}\\
%%  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d200_01}\\

@@

\afterpage{
\begin{figure*}
\small
\centering%
\begin{minipage}{0.49\linewidth}
  \texttt{N-p40-01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_RandB_N-p40-01}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{N-p40-02} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_RandB_N-p40-02}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{N-t59b11xx} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_IO_N-t59b11xx}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{N-t59d11xx} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_IO_N-t59d11xx}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{SGB\_N-sgb75\_01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_SGB_N-sgb75_01}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{SGB\_N-sgb75\_01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_SGB_N-sgb75_02}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{reC05} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec05_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{reC13} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec13_txt}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{reC19} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec19_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{reC31} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec31_txt}
\end{minipage}
\label{fig:results}
\caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on various instances.\label{fig:results}}
\vspace{10em}
\end{figure*}
}

@@

\myparagraph{Reproducibility} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
%  \vspace*{-1em}
\begin{acks}
%\paragraph*{Acknowledgements.} Blind
We would like to thank Hao Wang (Leiden University) for pointing us to the arguments of
\citep{EriPeaGar2019scalable}.
%
This article is based upon work from COST Action CA15140 `Improving Applicability of Nature-Inspired Optimisation by Joining Theory and Practice (ImAppNIO)' supported by COST (European Cooperation in Science and Technology).
%
M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government. 
%Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
  %   Scientists' Support Program}.
\end{acks}

>>>>

\author{Manuel López-Ibáñez}
\orcid{0000-0001-9974-1295}
\affiliation{
  \institution{University of Málaga}
  \city{Málaga}
  \country{Spain}
}
%\additionalaffiliation{University of Manchester, UK}
\email{manuel.lopez-ibanez@uma.es}

@@

\begin{figure}[!tb]
  \centering%
  \smaller
\begin{minipage}{0.49\linewidth}
  \centering
    \texttt{N-t59d11xx} (LOP)\\[-0.2ex]
    \includegraphics[width=\textwidth]{./img/heatmap_lop_IO_N-t59d11xx}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}
    \centering
    \texttt{N-sgb75.02} (LOP)\\[-0.2ex]
 \includegraphics[width=\textwidth]{./img/heatmap_lop_SGB_N-sgb75_02}
\end{minipage}\\\vskip 1em
\begin{minipage}{0.49\linewidth}
  \centering
  \texttt{reC13} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/heatmap_pfsp_rec13_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \centering
  \texttt{reC19} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/heatmap_pfsp_rec19_txt}
\end{minipage}
% \begin{minipage}{0.49\linewidth}
%   \centering
%   \texttt{kra32} (QAP)\\[-0.5ex]
% \includegraphics[width=\textwidth]{./img/heatmap_kra32_dat}
% \end{minipage}
\caption{Mean fitness (over 10 runs) of different configurations of $r_1$ and $r_2$ (darker is better).\label{fig:heatmaps}}
\end{figure}

@@

%  \includegraphics[width=\textwidth]{./img/synthetic_LOP_combined}

@@

%  \includegraphics[width=\textwidth]{./img/fitness_real_lop_RandB_N-p50-01}\\
%  \includegraphics[width=\textwidth]{./img/fitness_real_lop_RandA1_N-t1d100_01}\\
%  \includegraphics[width=\textwidth]{./img/fitness_real_lop_RandA1_N-t1d150_01}\\
%%  \includegraphics[width=\textwidth]{./img/fitness_real_lop_RandA1_N-t1d200_01}\\

@@

\afterpage{
\begin{figure*}
\small
\centering%
\begin{minipage}{0.49\linewidth}
  \texttt{N-p40-01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_lop_RandB_N-p40-01}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{N-p40-02} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_lop_RandB_N-p40-02}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{N-t59b11xx} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_lop_IO_N-t59b11xx}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{N-t59d11xx} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_lop_IO_N-t59d11xx}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{SGB\_N-sgb75\_01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_lop_SGB_N-sgb75_01}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{SGB\_N-sgb75\_01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_lop_SGB_N-sgb75_02}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{reC05} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_pfsp_rec05_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{reC13} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_pfsp_rec13_txt}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{reC19} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_pfsp_rec19_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{reC31} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{./img/fitness_pfsp_rec31_txt}
\end{minipage}
\label{fig:results}
\caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on various instances.\label{fig:results}}
\vspace{10em}
\end{figure*}
}

@@

\myparagraph{Reproducibility} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
%  \vspace*{-1em}
\begin{acks}
%\paragraph*{Acknowledgements.} Blind
  \smaller%
  We would like to thank Hao Wang (Leiden University) for pointing us to the arguments of
\citep{EriPeaGar2019scalable}.
%
This article is based upon work from COST Action CA15140 `Improving Applicability of Nature-Inspired Optimisation by Joining Theory and Practice (ImAppNIO)' supported by COST (European Cooperation in Science and Technology).
%
M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government. 
This work is also partially funded by the Elkartek program (Basque Government) and the Industrial Chair ``Machine Learning for Big Data'' from Télécom Paris, France. 
%Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
  %   Scientists' Support Program}.
\end{acks}
